\Large \bf Vigor: Toward Carrier-Grade Software Network Functions

### 2016-10-26 doc/paper/paper.tex
Put the new example into the paper.

% \begin{lstlisting}
% bool ring_full() {return SYMBOLIC("full");}

% bool ring_empty() {return SYMBOLIC("empty");}

% void ring_push_back(struct packet* p) {
%   ASSERT(p->port != 9); //Extra check.
% }

% void ring_pop_front(struct packet* p) {
%   FILL_SYMBOLIC(p, sizeof(struct packet), 
%                 "popped_packet");
%   ASSUME(p->port != 9);
% }
% \end{lstlisting}

int main() {
  struct packet p;
  while(LOOP(1)) {
    if (!ring_full())
      if (receive_packet(&p) && p.port != 9)
        ring_push_back(&p);
    if (!ring_empty() && can_send_packet()) {
      ring_pop_front(&p);
      ASSERT(p.port != 9);
      send_packet(&p);
    }
  }
  return 0;
}
\end{lstlisting}

@@

\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p);
/*@ requires ringp(r, ?lst) &*&
             lst != nil &*&
             p->port |-> _ &*&
             struct_packet_padding(p); @*/
/*@ ensures ringp(r, tail(lst)) &*&
            pktp(p, head(lst)); @*/
\end{lstlisting}

Note \code{pktp(p, head(lst));} predicate includes the \code{p->port != 9} property.

@@

\begin{lstlisting}
int port_0;
struct ring* arg1;
struct packet arg2;
//@ assume((9 == port_0));
arg2.port = port_0;
loop_invariant_produce(&(arg1));
bool ret1 = ring_full(arg1);
//@ assume(ret1 == false);
bool ret2 = ring_empty(arg1);
//@ assume(ret2 == false);

ring_pop_front(arg1, &(arg2));
//@ open pktp(&(arg2), _);
/*@ assert((false == (9 == arg2.port))); @*/
\end{lstlisting}

>>>>

\begin{lstlisting}
int main(int argc, char** argv) {
  struct packet p;
  struct ring *r = ring_create(CAP);
  if (!r) return 1;
  while(LOOP(1))
  {
    loop_iteration_begin(&r);
    if (!ring_full(r))
      if (receive_packet(&p) && p.port != 9)
        ring_push_back(r, &p);
    if (!ring_empty(r) && can_send_packet()) {
      ring_pop_front(r, &p);
      VIGOR_CHECK(p.port != 9);
      send_packet(&p);
    }
    loop_iteration_end(&r);
  }
  return 0;
}
\end{lstlisting}

\begin{lstlisting}
#define CAP 512
#define RING_CAPACITY 512

/*@
  fixpoint bool user_packet_property(packet p) {
    switch(p) { case packet(port): return port != 9; }
  }
  @*/

static bool packet_constraints(struct packet* p) {
  return p->port != 9;
}
\end{lstlisting}

@@

\begin{lstlisting}
void ring_pop_front(struct ring* r,
                    struct packet* p);
/*@ requires ringp(r, ?lst,
                   ?property, ?capacity) &*&
             lst != nil &*&
             packetp(p, _); @*/
/*@ ensures ringp(r, tail(lst),
                  property, capacity) &*&
            packetp(p, head(lst)) &*&
            true == property(head(lst)); @*/
\end{lstlisting}

Note that \code{property(head(lst));} in the post condition ensures \code{p->port != 9} property.

@@

\begin{lstlisting}
struct ring* arg1;
struct packet arg2;

loop_invariant_produce(&(arg1));
/*@ open loop_invariant(_); @*/
bool ret1 = ring_full(arg1);
//@ assume(ret1 == false);
bool ret2 = ring_empty(arg1);
//@ assume(ret2 == false);
//@ close packetp(&(arg2), packet((&(arg2))->port));

ring_pop_front(arg1, &(arg2));
//@ open packetp(&(arg2), _);

/*@ assert((false == (9 == arg2.port))); @*/
\end{lstlisting}
